dendro

### 2017-05-16 analysis/test-bai.Rmd
update

```{r, warning=FALSE, message=FALSE}
library("tidyverse")
library("stringr")
library("dplR")
library("knitr")
source(paste0(getwd(), '/script/R/bai_piovesan.R'))
source(paste0(getwd(), '/script/R/rw_byTree.R'))
```

@@

@@

ft <- ft %>% 
  mutate(elev = ifelse(id_focal %in% sj_lowcode, 'Low',
                       ifelse(id_focal %in% sj_highcode, 'High',
                              ifelse(id_focal %in% ca_lowcode, 'Low', 'High')))) %>%
  mutate(site = paste0(loc, '_', elev))
```

>>>>

```{r, warning=FALSE, message=FALSE}
library("tidyverse")
library("stringr")
library("dplR")
library("knitr")
library("detrendeR")
source(paste0(getwd(), '/script/R/bai_piovesan.R'))
source(paste0(getwd(), '/script/R/rw_byTree.R'))
```

@@

# Get only focal trees, and only selected variables 
ft <- compete %>% 
  filter(sp=='Focal') %>% 
  filter(id_focal!='Fresno') %>% 
  dplyr::select(id_focal, loc, dn_mm, height_cm)

@@

ft <- ft %>% 
  mutate(elev = as.factor(
    ifelse(id_focal %in% sj_lowcode, 'Low',
                       ifelse(id_focal %in% sj_highcode, 'High',
                              ifelse(id_focal %in% ca_lowcode, 'Low', 'High'))))) %>%
  mutate(site = as.factor(paste0(loc, '_', elev)))
```

### General statistics by site

```{r}
# Create subset to compare between sites 
caL <- ca[,c("SNB0101","SNB0102","SNB0201","SNB0202","SNB0301","SNB0302","SNB0401","SNB0402","SNB0501","SNB0502g",
             "SNB0601","SNB0602","SNB0701","SNB0702g","SNB0801g","SNB0802g","SNB0901g","SNB0902","SNB1001","SNB1002",
             "SNB2601","SNB2602","SNB2701","SNB2702g","SNB2801","SNB2802","SNB2901","SNB2902","SNB3001","SNB3002")]

caH <- ca[, c("SNB1101","SNB1102","SNB1201","SNB1202","SNB1301","SNB1302","SNB1401","SNB1402","SNB1501","SNB1502",
              "SNB1601","SNB1602","SNB1701","SNB1702","SNB1801","SNB1802","SNB1901","SNB1902","SNB2001","SNB2002g",
              "SNB2101","SNB2102","SNB2201g","SNB2202g","SNB2301g","SNB2302","SNB2401","SNB2402","SNB2501","SNB2502")]

sjL <- sj[, c("SNA0101","SNA0102","SNA0201","SNA0202","SNA0301","SNA0302","SNA0401","SNA0402","SNA0501","SNA0502",
              "SNA0601","SNA0602","SNA0603","SNA0701","SNA0702","SNA0801","SNA0802","SNA0901","SNA0902","SNA0903",
              "SNA1001","SNA1002","SNA1003")]
sjH <- sj[, c("SNA1101","SNA1102","SNA1103","SNA1201","SNA1202","SNA1203","SNA1301","SNA1302","SNA1303","SNA1401",
              "SNA1402","SNA1501","SNA1502","SNA1601","SNA1602","SNA1701","SNA1702","SNA1703","SNA1801","SNA1802",
              "SNA1901","SNA1902","SNA2001","SNA2003","SNA2002")]
```

### Dendrochronological summary 
```{r}
objects_rwl <- c('caL','caH','sjL','sjH')

out <- c()

for (i in objects_rwl){

  aux <- get(i)
  aux_stats <- rwi.stats(aux)

  aux_stats$site <- i

  out <- rbind(out, aux_stats)
  }

d <- rwl.report(ca)
